Carrier phase and amplitude estimation for phase shift keying using pilots and data

### 2014-05-26 response2.tex
added further to comments

\newcommand{\fracpart}[1]{\left\langle #1 \right\rangle}
\newcommand{\sfracpart}[1]{\langle #1 \rangle}
\newcommand{\round}[1]{\lfloor #1 \rceil}
\newcommand{\floor}[1]{\lfloor #1 \rfloor}
\newcommand{\ceil}[1]{\lceil #1 \rceil}
\newcommand{\reals}{{\mathbb R}}
\newcommand{\ints}{{\mathbb Z}}
\newcommand{\integers}{{\mathbb Z}}
\newcommand{\uy}{\underline{\bm{Y}}}
\newcommand{\uey}{\underline{Y}}
\newcommand{\sign}[1]{\mathtt{sign}(#1)}
\newcommand{\Qbf}{{\mathbf Q}}
\newcommand{\Bbf}{{\mathbf B}}
\newcommand{\Ibf}{{\mathbf I}}
\newcommand{\ybf}{{\mathbf y}}
\newcommand{\xbf}{{\mathbf x}}
\newcommand{\zbf}{{\mathbf z}}
\newcommand{\ebf}{{\mathbf e}}
\newcommand{\vbf}{{\mathbf v}}
\newcommand{\wbf}{{\mathbf w}}
\newcommand{\kbf}{{\mathbf k}}
\newcommand{\sbf}{{\mathbf s}}
\newcommand{\tbf}{{\mathbf t}}
\newcommand{\pbf}{{\mathbf p}}
\newcommand{\Pibf}{{\mathbf \Pi}}
\newcommand{\onebf}{{\mathbf 1}}
\newcommand{\fbf}{{\mathbf f}}
\newcommand{\ubf}{{\mathbf u}}

@@

\item \textbf{Comment:} p. 3: in continuous text I prefer the use of ``approached infinity'' rather than ``$\to \infty$'' \\
\textbf{Response:}

@@

\item \textbf{Comment:} p. 5 (and further throughout the text): ``pilots symbols" (with `s') and ``pilot symbols'' (without `s') are both used $\to$ use only 1, I prefer ``pilot symbols'' \\
\textbf{Response:}

\item \textbf{Comment:} I think it would be a good idea to specify the main notational conventions at the end of the introductory section \\
\textbf{Response:}

\item \textbf{Comment:} between (5) and (6): start new paragraph \\
\textbf{Response:}

\item \textbf{Comment:} before (6): drop the 'to' \\
\textbf{Response:}

\item \textbf{Comment:} before (7): change ``for given $\theta$'' to ``for given $\theta$ and $\rho$'' \\
\textbf{Response:}

\item \textbf{Comment:} what is the use of keeping the constants `A' and `B' in the expressions $\to$ can they not be dropped? \\
\textbf{Response:}

\item \textbf{Comment:} I would prefer to see comma's between two subindices; so, `$k,i$' rather than`'$ki$' \\
\textbf{Response:}

\item \textbf{Comment:} below (11) '$g_{ik}$' should be '$g_{ki}$' (change order of the subscripts) \\
\textbf{Response:}

\item \textbf{Comment:} I would prefer to see brackets around the functions of which the mean is computed (use of the operator $\mathbb E$) \\
\textbf{Response:}

\item \textbf{Comment:} p. 12: ``the amplitude estimation error with bias removed'' $\to$ bit strange formulation \\
\textbf{Response:}

@@

\item \textbf{Comment:} p. 15: the use of `A' as notation for a sample space is confusing since `A' has already been used as a constant \\
\textbf{Response:}

@@

\item \textbf{Comment:}  Eq. (14) would be easier to follow with the intermediate step inserted $\dots = (a_0s_i + w_i)/(a_0s_i) = \dots$ \\
\textbf{Response:}

@@

\item \textbf{Comment:}  The variable  ``a'' in the equation 2 is not defined in the text \\
\textbf{Response:}

\item \textbf{Comment:}  There are typografical errors in the words  ``multiple antenna'' in line 2, page 2, section 1 \\
\textbf{Response:}

\item \textbf{Comment:}  And also in the word ``receiver" in line 28 of the same page.
 \\
\textbf{Response:}

>>>>

\newcommand{\fracpart}[1]{\left\langle #1 \right\rangle}
\newcommand{\sfracpart}[1]{\langle #1 \rangle}
\newcommand{\round}[1]{\lfloor #1 \rceil}
\newcommand{\floor}[1]{\lfloor #1 \rfloor}
\newcommand{\ceil}[1]{\lceil #1 \rceil}
\newcommand{\abs}[1]{{\left\vert #1 \right\vert}}
\newcommand{\sabs}[1]{{\vert #1 \vert}}
\newcommand{\reals}{{\mathbb R}}
\newcommand{\ints}{{\mathbb Z}}
\newcommand{\integers}{{\mathbb Z}}
\newcommand{\uy}{\underline{\bm{Y}}}
\newcommand{\uey}{\underline{Y}}
\newcommand{\sign}[1]{\mathtt{sign}(#1)}
\newcommand{\Qbf}{{\mathbf Q}}
\newcommand{\Bbf}{{\mathbf B}}
\newcommand{\Ibf}{{\mathbf I}}
\newcommand{\ybf}{{\mathbf y}}
\newcommand{\xbf}{{\mathbf x}}
\newcommand{\zbf}{{\mathbf z}}
\newcommand{\ebf}{{\mathbf e}}
\newcommand{\vbf}{{\mathbf v}}
\newcommand{\wbf}{{\mathbf w}}
\newcommand{\kbf}{{\mathbf k}}
\newcommand{\sbf}{{\mathbf s}}
\newcommand{\tbf}{{\mathbf t}}
\newcommand{\pbf}{{\mathbf p}}
\newcommand{\Pibf}{{\mathbf \Pi}}
\newcommand{\onebf}{{\mathbf 1}}
\newcommand{\fbf}{{\mathbf f}}
\newcommand{\ubf}{{\mathbf u}}

@@

\item \textbf{Comment:} p. 3: in continuous text I prefer the use of ``approached infinity'' rather than ``$\to \infty$'' \\
\textbf{Response:} This change has been made wherever it occurs in the introduction, but not throughout the whole text. This is a personal preference of the authors.

@@

\item \textbf{Comment:} p. 5 (and further throughout the text): ``pilots symbols" (with `s') and ``pilot symbols'' (without `s') are both used $\to$ use only 1, I prefer ``pilot symbols'' \\
\textbf{Response:} All occurences of pilots symbols have been changed to pilot symbols.

\item \label{rev2:commentnotationsection} \textbf{Comment:} I think it would be a good idea to specify the main notational conventions at the end of the introductory section \\
\textbf{Response:} It is the authors preference to introduce notation as it is used in the text rather than in a dedicated notation section. %BLERG. This need to be done. It's connected with comment~\ref{rev2:commentE}.

\item \textbf{Comment:} between (5) and (6): start new paragraph \\
\textbf{Response:} The paragraph ends at ``\dots least squares estimator of the data symbols~\cite{Sweldens2001,Mackenthun1994}'' and the new paragraph begins with ``To see this, let $a = \rho e^{j\theta}$ \dots''

\item \textbf{Comment:} before (6): drop the 'to' \\
\textbf{Response:} Done.

\item \textbf{Comment:} before (7): change ``for given $\theta$'' to ``for given $\theta$ and $\rho$'' \\
\textbf{Response:} Done.

\item \textbf{Comment:} what is the use of keeping the constants `A' and `B' in the expressions $\to$ can they not be dropped? \\
\textbf{Response:} The constants are retained so that statements of equality, such as
\[
LS(\{d_i, i \in D\}) = A - \frac{1}{L}\abs{Y}^2
\]
are valid. For the purpose of minimisation the constants have no effect.  However, in this case, we feel that introducing notation to describe ``equivalent for the purpose of minimisation'' is more cumbersome than simply retaining constants in the few cases that they occur.

\item \textbf{Comment:} I would prefer to see comma's between two subindices; so, `$k,i$' rather than`'$ki$' \\
\textbf{Response:} Done.

\item \textbf{Comment:} below (11) '$g_{ik}$' should be '$g_{ki}$' (change order of the subscripts) \\
\textbf{Response:} Fixed.

\item \label{rev2:commentE} \textbf{Comment:} I would prefer to see brackets around the functions of which the mean is computed (use of the operator $\mathbb E$) \\
\textbf{Response:} BLERG.  Connected with comment~\ref{rev2:commentnotationsection}.

\item \textbf{Comment:} p. 12: ``the amplitude estimation error with bias removed'' $\to$ bit strange formulation \\
\textbf{Response:} This phrase has been removed.

@@

\item \textbf{Comment:} p. 15: the use of `A' as notation for a sample space is confusing since `A' has already been used as a constant \\
\textbf{Response:} $A$ has been replaced by $\Sigma$ and $A^\prime$ by $\Sigma^\prime$.

@@

\item \textbf{Comment:}  Eq. (14) would be easier to follow with the intermediate step inserted $\dots = (a_0s_i + w_i)/(a_0s_i) = \dots$ \\
\textbf{Response:} Done.

@@

\item \textbf{Comment:}  The variable  ``a'' in the equation 2 is not defined in the text \\
\textbf{Response:} In~\eqref{eq:LSdefn} the variable $a$ is an argument of the function $LS$, that is,
\[
\begin{split}
LS(a, &\{d_i, i \in D\}) = \sum_{i \in P \cup D} \abs{ y_i - a s_i }^2  \\
&= \sum_{i \in P} \abs{ y_i - a p_i }^2 + \sum_{i \in D} \abs{ y_i - a d_i }^2.
\end{split}
\]

\item \textbf{Comment:}  There are typografical errors in the words  ``multiple antenna'' in line 2, page 2, section 1 \\
\textbf{Response:} Fixed.

\item \textbf{Comment:}  And also in the word ``receiver" in line 28 of the same page.
 \\
\textbf{Response:} Fixed.
